Democracy, Public Support, and Measurement Uncertainty

### 2021-06-02 paper/dcpo_demsupport.Rmd
analysis all going through

```{r dcpoPointAJPS}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

# the readRDS produced "unknown format" error, very weild

df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(
         country = countrycode::countrycode(country, "country.name", "country.name"),
         regime = Vdem_regime > 1) %>% 
  filter(year >= first_year) # using trimmed data as Claassen

@@

```{r dcpoUncertaintyAJPS}
load(here("data", "dcpo_ajps_rubin.rda"))

df_dcpo <- dcpo_ajps_rubin %>% map(~ .)

@@

result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_dcpo, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

@@

```{r dcpoPointAPSR}
df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
  filter(year >= firstyear)

load(here::here("output", "estimates_dcpoMean.RDS"))

@@

```{r dcpoUncertaintyAPSR}
# ls_country <- levels(dcpo_input$data$kk)
# first_year <- min(dcpo_input$data$year)
# 
# df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
#   dcpo_theta$theta[anEntry,,] %>% 
#     reformat_dcpo_output("theta") %>% 
#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
#               by = c("year", "country")) %>%
#     left_join(df_controls, by = c("country", "year")) %>% 
#     plm::pdata.frame(index = c("country", "year"))
# })

## The same as in the previous chunk

@@

###Duble check the dataset--------------
ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoUncertainAPSR)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoUncertainAPSR)")
)

@@

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
load(here("output", "estimates_clsAPSR.RDS"))
result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))

>>>>

```{r dcpoMean}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

saveRDS(df_dcpoMean, file = here("data", "df_dcpoMean.RDS"))
```

```{r dcpoPointAJPS}
df_controls <- readRDS(here("data", "control_variables_ajps.rds")) %>% 
  mutate(country = countrycode::countrycode(country, "country.name", "country.name"),
         regime = Vdem_regime > 1) %>% 
  filter(year >= first_year) # using trimmed data as Claassen

@@

```{r dcpoUncertaintyAJPS}
df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
  .x[[.y]] %>%
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>%
    plm::pdata.frame(index = c("country", "year"))
}) # The code is to fit the embedded format of dcpo_ajps_rubin

@@

result_dcpoUncertain <- map(ls_mod, function(aMod){ # reading a model
  mod_eval <- function(aData) eval(parse(text = aMod))

  result <- map(df_dcpo, mod_eval)

@@

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))

@@

```{r dcpoPointAPSR}

df_dcpoMean <- readRDS(here("data", "df_dcpoMean.RDS"))

df_controls <- readRDS(here("data", "control_variables_apsr.rds")) %>% 
  mutate(country = countrycode::countrycode(country, "country.name", "country.name")) %>% 
  filter(year >= first_year)

@@

```{r data-dcpoUncertainAPSR}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>%
    reformat_dcpo_output("theta") %>%
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>%
    plm::pdata.frame(index = c("country", "year"))
})

saveRDS(df_dcpoUncertainAPSR, here("data", "df_dcpoUncertainAPSR.rds"))
```

```{r dcpoUncertaintyAPSR}
## The same as in the previous chunk

@@

@@

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
result_dcpoAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))
